%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\hypersetup{
    colorlinks=false,
    pdftitle={Williams, Rey - Resume [SWE]},
    pdfnewwindow=true
    }


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItems}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-6pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Rey Williams}} & Email : \href{mailto:reynaldomwilliams@gmail.com}{\underline{reynaldomwilliams@gmail.com}}\\
  & \href{https://www.linkedin.com/in/rey-williams/}{\underline{LinkedIn}} |
  \href{https://github.com/reywilliams}{\underline{GitHub}} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Florida Atlantic University}{Boca Raton, FL}
      {B.S. in Computer Science, Certificate \& Concentration in Data Science \& Artificial Intelligence (AI) | GPA: 3.9}
      
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Java, JavaScript, TypeScript, C++, C, Python,  SQL, CSS, C\#}
	\resumeSubItem{Frameworks/Platforms}{React-Redux, React Native, Node.js, Bootstrap, Jest, ASP.NET MVC, Azure}
        \resumeSubItem{Certifications}{
        \href{https://www.credly.com/badges/d68c53f0-344d-4a6e-a31a-878fa221a28c/public_url}{\underline{Azure Solutions Architect Expert (AZ 305)}}
        \href{https://www.credly.com/badges/0fe09b8c-f53c-439b-a47c-6ea09d50c88b/public_url}{\underline{Azure Admin (AZ 104)}},
        \href{https://www.credly.com/badges/32e35ccb-e7ea-4882-b00a-ea1d3e56ef06/public_url}{\underline{Azure AI Fdmtls (AI 900)}}}
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Microsoft}{Fargo, ND}
    {Cloud Support Engineer - Azure IaaS VM \& Storage}{August 2022 - September 2023}
        \resumeItemListStart
            \resumeItems{Supported Microsoft's top 500 strategic customers, ensuring seamless operation of their mission-critical/production systems on Azure, while providing essential technical guidance and implementing remediation steps to guarantee business continuity.}
            \resumeItems{Engaged in cross-business collaboration to improve the design and functionality of Azure products by identifying gaps and driving distinct improvements to help with issue deflection by $\sim$23\%.}
            \resumeItems{Identified as Azure Files Subject Matter Expert; created and maintained technical specification/scenario documentation for troubleshooting workflows in Azure Storage \& consulted on highly escalated cases, eliminating redundant engagement by 13\% \& troubleshooting hours for 100+ engineers.}
            \resumeItems{Consulted on and drove hundreds of cases to resolution, meeting service level agreements in 100\% of cases.}
            \resumeItems{Recognized in Monthly Employee Spotlight for immense first-year growth and career velocity.}
        \resumeItemListEnd
    \resumeSubheading
    {Origami Risk}{Chicago, IL}
    {Fullstack Software Engineer Intern}{May 2022 - August 2022}
        \resumeItemListStart
            \resumeItems{
            Provided various risk management, risk analysis, and insurance solutions across technologies such as ASP.NET MVC, SQL Server, C\#, HTML/CSS, and JavaScript to over 800 live clients across multiple sectors like healthcare, insurance carriers, risk pools, and manufacturing.}
            \resumeItems{Created an end-to-end component to streamline how organizations organize and conduct audits for risk assessments; allows for ~30\% faster execution of audits.}
            \resumeItems{Improved testing accuracy to 97\% across (almost 50\% increase) all cases through an extensive refactoring of almost 20 different test suites across all layers and domains.
            }
            \resumeItems{Built new components to support and manage client product implementations across all layers (database, services, web UI).}
        \resumeItemListEnd
    \resumeSubheading
    {Walmart Global Tech}{Bentonville, AR}
    {Frontend Software Engineer Intern}{June 2021 - August 2021}
        \resumeItemListStart
            \resumeItems{Organized, developed, and deployed integral components to support the release of the next
generation of point-of-sale and e-commerce components with technologies such as TypeScript, JavaScript, React, React-Redux, and React Native.}
            \resumeItems{Implemented component to move away from the use of static images and push towards dynamic image fetching/modules for proprietary marketing and media content REST API.}
            \resumeItems{Researched and documented the functionality of server-side caching to reduce bandwidth, reduce expenses, and deliver a quicker user experience on every transaction.}
            \resumeItems{Implemented component to handle the fetching of 100s of product data and dynamically render them
given store/site parameters alongside a full testing suite with 95\%+ coverage.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
%-----------WAVELENGTH-----------------
\resumeItem{\href{https://github.com/ReyWilliams/WavelengthPlatform}{\underline{Wavelength - Tutoring Web App}}}{}
\begin{description}[font=$\circ$]
\item {Designed and managed full-stack application created from scratch using modified MERN stack. Uses MongoDB for a serverless back-end. Designed and implemented flexible schema to express relationships between users and object entities like courses. Intended to mimic a tutoring coordination web application that connects students with tutors. Demo \textbf{\href{https://youtu.be/139RpHbwhKU}{\underline{here}}}.}
\item { Integrated Auth0's authentication API into the application, allowing users to securely log in and access protected resources and tailor their user experiences.}
\item {Uses Zoom API to facilitate communication and allow users to create and join Zoom calls on the web.}
\item {Uses Google Calendar API to allow users to create calendar entries for their sessions.}
\end{description}
%-----------Persistent Shopping Platform-----------------
\resumeItem{\href{https://github.com/ReyWilliams/ShoppingCart}{\underline{Persistent Shopping Platform}}}{}
\begin{description}[font=$\circ$]
\item {Designed and implemented an end-to-end shopping cart application with interactive GUI in Java. Demo \textbf{\href{https://youtu.be/88_xpOJGbVg}{\underline{here}}}.}
\item {Allows users to have a simplified shopping experience similar to popular web stores like Amazon. It allows for
persistence across multiple user accounts and updates product inventory and views that are given.}
\item {Used MVC (Model-View-Controller) architecture to separate the application's data, logic, and presentation layers.}
\item {Wrote unit tests using JUnit to ensure the reliability and performance of the application.}
\end{description}
\resumeSubHeadingListEnd

\end{document}
